SIR Model With Testing Flows and Isolation

### 2020-12-10 codes/ali_test_sir.Rmd
modulate the code, functions, plotting

```{r model inputs, message=FALSE}
params <- c(N0=1000000, beta=.8,gamma=1/3, omega=0.25, rho=0.01, #0.8, 1/3
             W_S=1, W_I=1, W_R=1, #weights
             p_S=0, p_I=1, p_R=0.5, #prob of waiting for being tested positive
            eta_w=0.02, eta_c=0.01, #isolation parameter 
            s=2 #eta_w/eta_c
            )
class(params) <- "params_pansim"
state_init <- c(S_u=params[["N0"]], S_n=0,
                I_u=1,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
sim_time <- seq(0,200,by=0.1)
```

@@

# DFE; analytic approach
Su <- Su_dfe(params)
Sn <- Sn_dfe(params)
state_dfe <- c(S_u=Su, S_n=Sn,
                I_u=0,I_n=0,I_p=0,I_t=0,
                R_u=0,R_n=0,R_p=0,R_t=0,
                N=0,P=0)
# check:
all.equal(c(state_dfe[["S_u"]],state_dfe[["S_n"]]),roots_dfe$root)
```

@@

```{r model_run, message=FALSE}
out <- run.sir(model=sir.model,
               params=update(params,beta=2),
               state=state_init,
               sim_time=sim_time)

@@

## BMB: FIXME: probably wrong but ... ???
## ggsave(p1_temp,filename = "R0contour_random.pdf" , path="../pix/")
ggsave(p1_temp,filename = "R0contour_TTI.pdf" , path="../pix/")

>>>>

```{r model inputs, message=FALSE}
source("params")
```

@@

# DFE; analytic approach
# Su <- Su_dfe(params)
# Sn <- Sn_dfe(params)
# state_dfe <- c(S_u=Su, S_n=Sn,
#                 I_u=0,I_n=0,I_p=0,I_t=0,
#                 R_u=0,R_n=0,R_p=0,R_t=0,
#                 N=0,P=0)
# check:
all.equal(c(state_dfe[["S_u"]],state_dfe[["S_n"]]),roots_dfe$root)
```

@@

```{r model_run, message=FALSE}
sim_time <- seq(0,200,by=0.1)

out <- run.sir(model=sir.model,
               params=update(params,beta=2),
               state=state_init,
               sim_time=sim_time)

@@

## BMB: FIXME: probably wrong but ... ???
## ggsave(p1_temp,filename = "R0contour_random.pdf" , path="../pix/")
